SFJ: An implementation of Semantic Featherweight Java

### 2020-04-22 conference/camera ready/paper.tex
on complexity

>>>>

Finally, a note on complexity.
The complexity of \autoref{alg:types} is $\mathcal{O}(n)$, and the complexity of \autoref{alg:subtyping} is $\mathcal{O}(n^{2})$, with $n$ being the size of the input.
The reason for an exponential complexity \autoref{alg:subtyping} is due to the symmetric check of structural subtyping between a $class$ and an $existingClass$ in $relation$.
Notice that if we were to only work with nominal subtyping, then we only require traversing the class hierarchy once,  which gives an $\mathcal{O}(n)$ complexity.

\subsection{Type system for SFJ}
The subtyping relation generated by \autoref{alg:subtyping} is used in the type system for SFJ terms, given in \autoref{sec:terms}.
The complete type system and its properties are presented in relevant work \cite{Dardha2013,Dardha2017} and are beyond the scope of this paper.
Let us briefly comment on typing expressions in SFJ.
Field access $e.a$, method call $e.m(e)$ and object creation $\synnew C(\wt{e})$ are typed in the same way as in Java.
Let us comment on constants...
